Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-05-25 Manuscript.Rmd
cleaned up comments throughout the manuscript, hoping to improve readability

---
title: 'Individual heterogeneity in the functional network topography of medial prefrontal cortex'
author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
output:
  pdf_document: 
    keep_tex: true
    highlight: haddock
bibliography: mPFC_paper.bib
csl: apa.csl
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage[left]{lineno}
    - \linenumbers
    - \usepackage{float}
    - \newcommand{\beginsupplement}{ 
        \setcounter{table}{0}  
        \renewcommand{\thetable}{S\arabic{table}} 
        \setcounter{figure}{0} 
        \renewcommand{\thefigure}{S\arabic{figure}}
      }

@@

# general options
threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
permuting <- FALSE # show meta-analysis permutation progress? (SLOW)

@@

## produce one permutation instance of the meta-analysis (so it can be fed to mclapply for quicker results)
metaPerm <- function(list1 = studyList_sv, list2 = studyList_DN, labels = Yeo_labels, perm = 1) {

@@

# Create a vector ready to be used for HCP data (32k CIFTI surface)
# The input should be the summary from community partitioning
# Once this is created, go to the terminal and input something like this
# wb_command -cifti-convert -from-text dataforCifti.txt 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii testCifti.dscalar.nii
# Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
HCPOut <- function(Data = DNval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){

@@

# Permutation analysis
# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
# Load the coordinates as studies in a list, because for the contrast the studies are permuted
# Use table(unlist(list)) to get the counts in that case
setwd('./metaresultsPOS')
templist <- dir()
studyList_sv <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())

@@

# optional because it can take a long time to run
if (permuting) {

@@

``` {r Load Summary Data}
# Load data
setwd('./Summary/')
temp <- list.files()
subjList <- sapply(temp, substring, first = 1, last = 6)
Summaries <- lapply(temp, read.csv)
nSubj <- length(Summaries)
nVertices <- nrow(Summaries[[1]]) # in case I need the number of vertices included per brain

@@

``` {r Partition comparison: all 2, echo = FALSE, message = FALSE, cache = TRUE}
## Community number evaluation (across and within methods)
# ARI between methods
RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary", "Membership"), nSubjects = nSubj, subjNames = subjList)

# Number of communities per subject for modularity
nModularity <- sapply(Summaries, function(data) {max(data$Membership)}) # n of estimated communities by modularity

@@

## Across subjects
# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
RI_all_between_lowtri <- RI_all_between[lower.tri(RI_all_between)]

posteriorIndx <- Summaries[[1]]$y < 0
tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)

# Let's compare stuff
testPCC <- RI_PCC[lower.tri(RI_PCC)]
testPFC <- RI_PFC[lower.tri(RI_PFC)]
Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
mPFCvs0_wilcox <- wilcox.test(testPFC) # is the mPFC agreement above chance?
mPFCvs0_ES <- DescTools::CohenD(testPFC)

@@

``` {r Variability per subject: Overall, echo = FALSE, message = FALSE, cache = TRUE}
# Load files
setwd('./Sliding_window/')
temp <- list.files(pattern = '*Comparisons.csv')
SC <- lapply(temp, read.csv2)
temp <- list.files(pattern = '*Values.csv')
SVals <- lapply(temp, read.csv2)

@@

``` {r Variability per subject: PCC vs mPFC, echo = FALSE, message = FALSE, cache = TRUE}
## Check stability for PCC and mPFC separately
# Get the sliding values for PCC and PFC separately
tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)

@@

for (subj in seq(nSubj)) {
  tempPCC <- numeric()
  tempPFC <- numeric()
  nWins <- ncol(tempSW_PCC[[subj]])
  for (Win in seq(nWins)) {
    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][, Win], adjust = T)
    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][, Win], adjust = T)
  }
  dfPCC <- data.frame(SubjID = rep(subjList[subj], nWins),
                      Window = seq(nWins),
                      Index = tempPCC)
  dfPFC <- data.frame(SubjID = rep(subjList[subj], nWins),
                      Window = seq(nWins),
                      Index = tempPFC)
  SC_PCC <- rbind(SC_PCC, dfPCC)
  SC_PFC <- rbind(SC_PFC, dfPFC)
}

SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
SC_PCC_summary$SD <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = sd)$x
SC_PCC_summary$Region <- rep("PCC", nSubj)
SC_PFC_summary <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = mean)
SC_PFC_summary$SD <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = sd)$x
SC_PFC_summary$Region <- rep("mPFC", nSubj)
SC_PCCPFC_summary <- rbind(SC_PFC_summary, SC_PCC_summary)
colnames(SC_PCCPFC_summary) <- list("SubjID", "Index", "SD", "Region")
rm(SC_PCC_summary, SC_PFC_summary)

@@

posteriorIndx <- Summaries[[1]]$y < 0
tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)

# Let's compare stuff
testPCC <- RI_PCC[lower.tri(RI_PCC)]
testPFC <- RI_PFC[lower.tri(RI_PFC)]
Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.

# To get the rate of stability per vertex across subjects
FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
FV <- do.call(cbind, lapply(Summaries, "[[", "FiedlerVec"))
FBS <- rowMeans(FB)
FBS[FBS < 0.5] <- 1 - FBS[FBS < 0.5]

@@

# Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
# Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we're manually reverting it after visual inspection
revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "108525_H2", "156637_H1")
for (subj in revertSubjs) {
  indx <- grep(subj, subjList_halves)
  Summaries_halves[[indx]] <- transform(Summaries_halves[[indx]], FiedlerVec = FiedlerVec * -1)
}
Summaries_halves_unthresh <- Summaries_halves

@@

# # Select 10 subjects from the sample to plot
# selectSubj <- seq(40)
# subjList_sess_plot <- subjList_sess[selectSubj]
# Summaries_sess_plot <- Summaries_sess[selectSubj]
# 
# 
# # Across subjects (just for plotting)
# RI_all_between_sess_plot <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
# tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
# tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
# RI_PFC_sess_plot <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
# RI_PCC_sess_plot <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
```

@@

``` {r Partition comparison: session ratios, echo = FALSE, message = FALSE, cache = TRUE}
## Brain storming:
## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
## Perhaps a more interresting idea would be to generate an index of variance within/between subject
## These are just attempts at that are not perfect:

# 1) Ratio of mean within subject sessions over between subject ones (per-subject)
# Overall
# Split the within-subject session RI values per subject
temp <- ceiling(seq_along(Sess_overallComparison[[1]])/6)
withinSubjVals <- split(Sess_overallComparison[[1]], temp)

@@

``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
## Between halves analysis for correlation and communities (mPFC only)
# Spearman to avoid issues with the differences in value ranges
unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- unthreshComm_PFC_halves_plot
D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1,D2)
subjList_halves_plot <- rep(best$SubjID, each = 2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))

@@

``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
# Compare correlation with community approach on mPFC
tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
tempCor <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
tempBoth <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
prepostComp <- melt(prepostComp)
colnames(prepostComp) <- c("Approach", "Correlation")
prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
prepostComp_ES <- cohenD(tempComm, tempCor)
```

@@

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Meta-analysis results. A: Proportion of times each ROI was reported in the valuation and DN literatures. B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details). Areas in blue represent the remaining search space."}
# Change to inflated eventually
include_graphics("./Images/ROIS.png")
```

@@

```{r Representative partitioning (Fig. 2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
# if you want to rescale the range of values, use scales::rescale(vecot, c(min, max))
include_graphics("./Images/FB_FV_example.png")
```

@@

```
\bigskip

>>>>

---
title: 'Individual heterogeneity in the functional network topography of medial prefrontal cortex'
author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
output:
  pdf_document: 
    keep_tex: false
    highlight: haddock
bibliography: mPFC_paper.bib
csl: apa.csl
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage[left]{lineno}
    - \linenumbers
    - \usepackage{float}
    - \newcommand{\beginsupplement}{ 
        \setcounter{table}{0}  
        \renewcommand{\thetable}{S\arabic{table}} 
        \setcounter{figure}{0} 
        \renewcommand{\thefigure}{S\arabic{figure}}
      }

@@

# general options
threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
permute <- FALSE # show meta-analysis permutation progress? (SLOW)

@@

## produce one permutation instance of the meta-analysis (so it can be fed to mclapply for faster results)
metaPerm <- function(list1 = studyList_sv, list2 = studyList_DN, labels = Yeo_labels, perm = 1) {

@@

# Create a vector ready to be used for HCP data (32k CIFTI surface)
# The input should be the summary from community partitioning
# Once this is created, go to the terminal and input something like this
# wb_command -cifti-convert -from-text dataforCifti.txt testSubj.dscalar.nii testCifti.dscalar.nii
# testSubj can be found under the `Basic_files` in the repo
HCPOut <- function(Data = DNval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){

@@

## Permutation analysis
# load parcels reported per study for each corpus
setwd('./metaresultsPOS')
templist <- dir()
studyList_sv <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())

@@

# optional because it can take a long time to run
if (permute) {

@@

``` {r Load Summary Data}
# Load data, create a subject list, get the total n, and the number of vertices
setwd('./Summary/')
temp <- list.files()
subjList <- sapply(temp, substring, first = 1, last = 6)
Summaries <- lapply(temp, read.csv)
nSubj <- length(Summaries)
nVertices <- nrow(Summaries[[1]])

@@

``` {r Partition comparison: all 2, echo = FALSE, message = FALSE, cache = TRUE}
## Community number evaluation (across and within methods)
# ARI between methods (membership = modularity assignment)
RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary", "Membership"), nSubjects = nSubj, subjNames = subjList)

# Number of communities per subject for modularity
nModularity <- sapply(Summaries, function(data) {max(data$Membership)})

@@

# ARI among individuals
# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
RI_all_between_lowtri <- RI_all_between[lower.tri(RI_all_between)]

# and now ARI among individuals per region (PCC or mPFC)
posteriorIndx <- Summaries[[1]]$y < 0
tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)

# Let's sttistically compare stuff
testPCC <- RI_PCC[lower.tri(RI_PCC)]
testPFC <- RI_PFC[lower.tri(RI_PFC)]
Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) 
mPFCvs0_wilcox <- wilcox.test(testPFC) # is the mPFC agreement above chance?
mPFCvs0_ES <- cohenD(testPFC)

@@

``` {r Variability per subject: Overall, echo = FALSE, message = FALSE, cache = TRUE}
# Load files
# these include the community assignment per window, as well as the agreement per window vs total partitioning
setwd('./Sliding_window/')
temp <- list.files(pattern = '*Comparisons.csv')
SC <- lapply(temp, read.csv2)
temp <- list.files(pattern = '*Values.csv')
SVals <- lapply(temp, read.csv2)

@@

``` {r Variability per subject: PCC vs mPFC, echo = FALSE, message = FALSE, cache = TRUE}
## Check variability for PCC and mPFC separately
tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)

@@

# compare the PCC and mPFC partitionings with those produced per window
for (subj in seq(nSubj)) {
  tempPCC <- numeric()
  tempPFC <- numeric()
  nWins <- ncol(tempSW_PCC[[subj]])
  for (Win in seq(nWins)) {
    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][, Win], adjust = T)
    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][, Win], adjust = T)
  }
  dfPCC <- data.frame(SubjID = rep(subjList[subj], nWins),
                      Window = seq(nWins),
                      Index = tempPCC)
  dfPFC <- data.frame(SubjID = rep(subjList[subj], nWins),
                      Window = seq(nWins),
                      Index = tempPFC)
  SC_PCC <- rbind(SC_PCC, dfPCC)
  SC_PFC <- rbind(SC_PFC, dfPFC)
}

# and get descriptives for all individuals
SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
SC_PCC_summary$SD <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = sd)$x
SC_PCC_summary$Region <- rep("PCC", nSubj)
SC_PFC_summary <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = mean)
SC_PFC_summary$SD <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = sd)$x
SC_PFC_summary$Region <- rep("mPFC", nSubj)
SC_PCCPFC_summary <- rbind(SC_PFC_summary, SC_PCC_summary)
colnames(SC_PCCPFC_summary) <- list("SubjID", "Index", "SD", "Region")
rm(SC_PCC_summary, SC_PFC_summary)

@@

# ARI among subjects for each region separately
posteriorIndx <- Summaries[[1]]$y < 0
tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)

# Let's statistically compare stuff
testPCC <- RI_PCC[lower.tri(RI_PCC)]
testPFC <- RI_PFC[lower.tri(RI_PFC)]
Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC)

# To get the rate of stability per vertex across subjects (used for plotting)
FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
FV <- do.call(cbind, lapply(Summaries, "[[", "FiedlerVec"))
FBS <- rowMeans(FB)
FBS[FBS < 0.5] <- 1 - FBS[FBS < 0.5]

@@

# Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
# Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we manually reverted it after visual inspection
revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "108525_H2", "156637_H1")
for (subj in revertSubjs) {
  indx <- grep(subj, subjList_halves)
  Summaries_halves[[indx]] <- transform(Summaries_halves[[indx]], FiedlerVec = FiedlerVec * -1)
}
Summaries_halves_unthresh <- Summaries_halves

@@

@@

``` {r Partition comparison: session ratios, echo = FALSE, message = FALSE, cache = TRUE}
# Ratio of mean within subject sessions over between subject ones (per-subject)
# Overall
# Split the within-subject session RI values per subject
temp <- ceiling(seq_along(Sess_overallComparison[[1]])/6)
withinSubjVals <- split(Sess_overallComparison[[1]], temp)

@@

``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
## Between halves analysis for correlation and communities (mPFC only)
# Spearman to avoid issues with the differences in value ranges
unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- unthreshComm_PFC_halves_plot
D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1, D2)
subjList_halves_plot <- rep(best$SubjID, each = 2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))

@@

``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
# Compare correlation with community approach on mPFC
# correlations among methods
tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
tempCor <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
tempBoth <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))

# put together in a data frame
prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
prepostComp <- melt(prepostComp)
colnames(prepostComp) <- c("Approach", "Correlation")

# paired permutations and effect sizes for within-subj perm vs corr
prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
prepostComp_ES <- cohenD(tempComm, tempCor)
```

@@

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Meta-analysis results. A: Proportion of times each ROI was reported in the valuation and DN literatures. B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details). Areas in blue represent the remaining search space."}
# brain images were produced using the HCP wb_view. 
# see the function HCPOut for details on how they were transferred from R to CIFTI
include_graphics("./Images/ROIS.png")
```

@@

```{r Representative partitioning (Fig. 2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
include_graphics("./Images/FB_FV_example.png")
```

@@
